Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-12-14 paper/main.tex
Added supercop compiler flags discussion

%TODO: Vi har andre compiler argumenter - dette må diskuteres

>>>>

\paragraph{Extra compiler flags}
%TODO: Vi har andre compiler argumenter - dette må diskuteres
We do not compile the candidate implementation with the exact same arguments
that is used in \ac{SUPERCOP}, most notably we append the -fPIC flag. This flag
creates position-independant-code, in other words machine instruction code that
can execute properly regardless of where in memory it resides. This will make
one less register available on the x86 architecture. While we cannot directly
prove that this will affect performance of the implementations. We do however
suspect it. A person writing an optimization for \ac{SUPERCOP} will have to
balance his use of resources, among them registers, to achieve maximum speed.
The loss of one register will then give a performance penalty.
